---
title: "Linear Models"
author: Yuqi Wang
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Import data
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

## Fit a model
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()

# fit a model

fit = lm(price ~ stars + borough, data = nyc_airbnb)
```


Let's look at the result ...
```{r}
fit

summary(fit) # we get more info from this
summary(fit)$coef

coef(fit)
residuals(fit)
```

Let's look at the result better ...
```{r}
broom::glance(fit) # provides the most useful information

broom::tidy(fit) %>% # provides the estimates, sd, p-value, this is a dataframe
  select(-std.error, -statistic) %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  knitr::kable(digits = 3)
```


# Be in control of factors

borough variable is a character variable. In regression and in ggplot, it automatically converts to a factor variable, so Bronx is always the reference.

```{r}
nyc_airbnb =
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  )

nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()

fit = lm(price ~ stars + borough, data = nyc_airbnb)

broom::tidy(fit) # Now, the reference group has changed.
broom::glance(fit)
```

## Diagnostics

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% # add residual column
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  ylim(-500, 1500)

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()+
  facet_wrap(. ~ borough)
```

## Hypothesis tests

This does t-test by default
```{r}
fit %>% 
  broom::tidy()
```

What about the significance of `borough`

```{r}
fit_null = lm(price ~ stars, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```

## nest data, fit models


This is pretty formal and complex
```{r}
lm(price ~ stars*borough + room_type*borough, data = nyc_airbnb)

broom::tidy(fit)
```

This is more exploratory but maybe easier to understand

```{r}
nyc_airbnb %>% 
  nest(data = -borough) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(term != "(intercept)") %>% 
  select(borough, term, estimate) %>% 
  pivot_wider(names_from = borough,
              values_from = estimate)
  
```

Let's nest even more ...
```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) +
  geom_point() +
  facet_wrap(. ~ term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
  
```




